---
title: "Final_Project_MISDI_Codecamp"
author: "Eleni"
date: "2023-06-22"
output: html_document
---

```{r}

# load libraries (quietly stops all the messages appearing)
library(readr, quietly = TRUE)
library(dplyr, quietly = TRUE)
library(ggplot2)
library(DT, quietly = TRUE)

# load imdb and bechdel
movies_imdb <- read_csv("https://raw.githubusercontent.com/andrewmoles2/rTrainIntroduction/main/r-data-wrangling-1/data/IMDb%20movies.csv")

bechdel <- read_csv("https://raw.githubusercontent.com/andrewmoles2/rTrainIntroduction/main/r-data-wrangling-1/data/raw_bechdel.csv")

# fix imdb id key
movies_imdb$imdb_title_id <- parse_number(movies_imdb$imdb_title_id)

# join data (left join)
imdb_bechdel <- left_join(x = movies_imdb, y = bechdel,
                          by = c("imdb_title_id" = "imdb_id", "year", "title"))

imdb_bechdel

Country1 <- imdb_bechdel %>% filter(genre %in% c("Comedy", "Drama","Thriller","Horror", "Mystery","Biography"))
Country1

Country1 %>%
  count(genre, sort = TRUE)

Country_plot <- ggplot(Country1, aes(x=year, y=genre )) +
  geom_hex(aes(x=year, y=genre)) +
  labs(title= "Genres Across Countries Throughout The Years") + 
  theme_minimal(base_size = 12)

Country_plot
```

                                                                                                


```{r}

# total movies by country- which country makes the most movies?

# Load the dplyr package
library(dplyr)

# Group the data by 'country' and calculate the count of movies per country
movie_counts <- imdb_bechdel %>%
  group_by(country) %>%
  summarize(total_count = n())

movie_counts

# Print the result
print(movie_counts)
```

```{r}

# Load the ggplot2 library
library(ggplot2)


# creating a graph to see budget and voting for 150 movies

filtered <- head(imdb_bechdel, 50)
filtered_data <- imdb_bechdel[1:150,]

filtered$budget_clean <- parse_number(filtered$budget)

# Create a scatter plot

ggplot(filtered, aes(x = avg_vote, y = budget_clean )) +
  geom_point(colour = "#A782C1") +
  labs(title = "Scatter Plot of average vote vs budget",
       x = "avg_vote",
       y = "budget") +
  theme_light() +
  scale_y_continuous(labels = scales::comma)

column_data_type <- class(imbd_bechdel$budget)
print(column_data_type)

# Change a column's data type to numeric
imbd_bechdel$budget <- as.numeric(imbd_bechdel$budget)
imdb_bechdel
```

# Libraries
library(tidyverse)
library(hrbrthemes)
library(plotly)
library(patchwork)
library(babynames)
library(viridis)

# Load dataset from github
data <- read.table("https://raw.githubusercontent.com/holtzy/data_to_viz/master/Example_dataset/3_TwoNumOrdered.csv", header=T)
data$date <- as.Date(data$date)

# plot
data %>%
  ggplot( aes(x=date, y=value)) +
    geom_area(fill="#69b3a2", alpha=0.5) +
    geom_line(color="#69b3a2") +
    ggtitle("Evolution of Bitcoin price") +
    ylab("bitcoin price ($)") +
    theme_ipsum()
#  count per type of movie for specific movie categories 

newdataset <- imdb_bechdel %>% filter(genre %in% c("Comedy", "Drama","Thriller","Horror", "Mystery","Biography"))
newdataset


movie_counts <- newdataset %>%
  group_by(genre) %>%
  summarize(total_count = n())

movie_counts

# Load the dplyr library
library(dplyr)

# Group the dataset by genre and calculate the average budget per genre
genre_avg_budget <- newdataset %>%
  group_by(genre) %>%
  summarize(budget = mean(budget))

# View the resulting grouped dataset
genre_avg_budget


# Load the ggplot2 library
library(ggplot2)

# Create a circular barchart with a light color palette
ggplot(data = movie_counts, aes(x = "", y = total_count, fill = genre)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(title = "Pie chart of Movie Counts by Genre",
       x = NULL, y = NULL) +
  scale_fill_brewer(palette = "Pastel1") +
  theme_void()
  
  #  lollipop
  
  # Create a lollipop graph with a light color palette
ggplot(data = movie_counts, aes(x = genre, y = total_count, fill = genre)) +
  geom_segment(aes(x = genre, xend = genre, y = 0, yend = total_count), color = "gray50") +
  geom_point(color = "steelblue", size = 3, shape = 21, fill = "white") +
  labs(title = "Lollipop Graph of Movie Counts by Genre",
       x = "Genre", y = "Count") +
  scale_fill_brewer(palette = "Pastel1") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))






